---
title: "Users within 100 kms of Dublin office"
author: "Abhimanyu Hazarika"
date: "December 16, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=TRUE}
library("jsonlite")

```

## Dataset Import

The user data in JSON format, stored in a text file(gistfile1.txt) is imported using the jsonlite library in R


```{r retrieveJSON}
#set the working directory
setwd("U:/IntercomTest") 

# Retrieving the user data stored in JSON format
data<-stream_in(file("gistfile1.txt"))

```
```{r displayData, echo=FALSE}
data

```

## Degree to Radian conversion
The latitude and longitude values of users address and Dublin office address are converted into radian using the below function

```{r degree2radian}
deg2rad <- function(deg) return(deg*pi/180)
# Converting the user's latitude and longitude from degree to radian
data$latitude <- deg2rad(as.numeric(data$latitude))
data$longitude <- deg2rad(as.numeric(data$longitude))
```
```{r displayData2, echo=FALSE}
data

```

## Geo distance calculation
Using Spherical Law of Cosines, the distance between two coordinates are calculated

```{r distance, echo=TRUE}
# Function to calculate the geo distance between User's latitude/longitude and Dublin office 
# using Spherical Law of Cosines
distance <- function(usrLong, usrLat) {
  officeLong=deg2rad(-6.257664) #Longitude of Intercom's Dublin office in degree
  officeLat<-deg2rad(53.339428) #Latitude of Intercom's Dublin office in degree
  R <- 6371 # Mean radius of Earth
  dist <- acos(sin(usrLat)*sin(officeLat) + cos(usrLat)*cos(officeLat) * cos(officeLong-usrLong)) * R
  return(dist) # Returning distance in kms
}
```

## Distance of each user from Dublin office

The distacne of each user in the dataset is added to the dataset

```{r column_distance, echo=TRUE}
# Adding column distance containing distance of the user from Intercom's Dublin office
data$distance<-distance(data$longitude, data$latitude)
```
```{r displayData3, echo=FALSE}
data

```

## Users within 100 kms of Dublin office

Filtering users who are within 100kms of Intercom's Dublin office. Sorting the list in the ascending  order of User ID.

```{r users100kms, echo=TRUE}
# Selecting only the user_id and name of the customers who live within 100 kms from Intercom's Dublin office
data<-data[data$distance <= 100, c("user_id","name")] 

# Putting the data in ascending order of user id
data <-data[order(data$user_id),]
```
```{r displayData4, echo=FALSE}
data

```

## Export user list to CSV

The CSV file containg the required data is stored in the working directory.

```{r writeCsv, echo=TRUE}

#Export the data into a CSV file
write.csv(data,file='usersWithin100kms.csv')
```